---
title: "Course Summary"
author: "Dan Gaile"
date: "October 21, 2016"
output: html_document
---

## Day 1: Packages and Version Control

We learned to create a package using [devtools][1]. The way to get started is to create the skeleton of a project using 
```
library(devtools)
create("Elbo")

``` 

This creates a directory with a couple files and a folder. We then did the following:

1. The DESCRIPTION file contains info about the package; we edited it for our purposes.
2. We looked at the NAMESPACE, but didn't touch it.
3. We created our first function in the R folder, `hi()`

We then used the package [roxygen2][] to add documentation to the function, including information about parameters and return values. We also used tags (`@export`) to indicate that we wanted to 'export' the function.

Note that when a label is defined, we can use it again: [roxygen2][] is really neat!


We also learned to managae our source coude using [github][]

Here is the result of our work:

```{r our-package}
library(Elbo)
hi("Dan")
```

## Day 2: Classic, Rich, and Tidy data

'Classic' data is represented as a `data.frame()` with samples as rows and features as columns.

```{r}
pdatfl="C://Users/dpgaile.AD/Dropbox/Work/Class/MorganRlib/Oct05/ALL-phenoData.csv"
exprfl="C://Users/dpgaile.AD/Dropbox/Work/Class/MorganRlib/Oct05/ALL-expression.csv"
classic <- input_classic(pdatfl, exprfl)
classic[1:5, c(1:3, 22:24)]
```

```{r}
hist(colMeans(classic[,-(1:22)]))
```


[1]: https://cran.r-project.org/package=devtools
[roxygen2]: https://cran.r-project.org/package=roxygen2
[github]: https://cran.r-project.org/package=github








